analysis

### 2019-12-09 03_Preliminary_analysis.Rmd
Corrections and additions to make easier for flow.

First lets investigate the difference in the effect of the type of fungicide on proportion of yield saved?

@@

#### Fungicide Doses

@@

There is much variation in the propiconazole dose, lets inspect the difference in yields for each dose.

```{r PropiDoseEffect}
PM_MB_means %>%
   filter(fungicide_ai == "propiconazole") %>%
   ggplot(aes(x = relevel(as.factor(dose_ai.ha),"62.5"), y = prop_YG)) +
   xlab("Dose (g ai/ha)") +
   ggtitle(label = "Yield for each respective propiconazole dose") +
   geom_boxplot() +
   scale_fill_usq() +
   scale_colour_usq() +
   theme_usq()

@@

PM_MB_means[PM_MB_means$fungicide_ai == "control"
               ,]

>>>>

First lets investigate the difference in the effect of the type of fungicide on proportion of yield saved. Proportion of yield saved is used in attempt to reduce variation between trials.

@@

There is a small yield effect when applying fungicide and it is unclear how much a second spray improves yield saved. Interestingly Sulpur sprays might be worth investigating when sprayed twice.

#### Fungicide Doses  
We should check that all fungicide doses that were used were roughly the same if we are to compare between trials were dose might be different.

@@

There is a large amount of variation in the propiconazole dose, lets inspect the difference in yields for each dose.

```{r PropiDoseEffect}
PM_MB_means %>%
   filter(fungicide_ai == "propiconazole") %>%
   ggplot(aes(x = relevel(as.factor(dose_ai.ha),"62.5"), y = prop_YG)) +
   xlab("Dose (g ai/ha)") +
   ggtitle(label = "Yield for each respective propiconazole dose") +
   geom_boxplot() +
   scale_fill_usq() +
   scale_colour_usq() +
   theme_usq()
```

Which studies used which doses?

```{r}

@@
